---
title: "Introduction to Data Science - HW 2"
author: "Gabriel Carlson- `gcarlson8249@floridapoly.edu`"
output: html_notebook
---



# Problem 1 (30 points)

During class you completed an activity in which you practiced `git` commands and operations (such as forking a repository, cloning it using `git clone`, and uploading changes using `git push`).

In this exercise you are asked to modify the `flpoly_student.md` file you worked during class, and format it using the **markdown** tools discussed in class. You must **create a table** that shows the courses you are currently enrolled in, using for the headers of the table: 

- Prefix: in bold letters (such as **COP**)
- Number: in bold letters (such as **2073**)
- Name: in italics (such as _Introduction to Data Science_)
- Credits (such as 3)

a. Make sure your GitHub repo (`flpoly_ds_course/`) shows the results of your updated file (remember to use the commands `git add .` , `git commit -m "YOUR MESSAGE"`, and `git push`) 

b. Include a link to your GitHub repo in this document.
[Link to github repo](https://github.com/Gabec1015/flpoly_ds_course/blob/main/flpoly_student.md)


c. Take a screenshot of the GitHub repo, add the screenshot file to the repo, and include it in this document (review how to insert a picture using markdown)

![Picture of Repo Here]()
# Problem 2 (30 points)

For this problem, you are asked to create a list of **3 concepts** you have learned about so far this semester, for at least 2 of the courses you are currently taking. Include the name of the course as a sub-heading (that is, using `##`), and the concepts as an unordered list. Include a link to information about at least one of the concept you listed (for example a link to the Wikipedia page about that concept/topics).

`##Introduction to data Science##`
How to pull edit and push a file from a Github repository.[Example here](https://www.atlassian.com/git/tutorials/syncing/git-pull)
How to Use R markdown techniques.
How to use Text formatting.


`##Introduction to Business Finance##`
How to calculate Interest rates on a loan.
Different levels of the federal reserve system.[Example here](https://www.federalreserve.gov/aboutthefed/structure-federal-reserve-system.htm#:~:text=There%20are%20three%20key%20entities,Open%20Market%20Committee%20(FOMC).)
How treasury notes work. 



# Problem 3 (40 points)

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains your preferred name.
```{r}
#Assign name to variable 
my_name <- nchar("Gabriel")
```
(b) Create a variable called `name_length` that holds how many letters are in `my_name`.
```{r}
#Assign length to variable
name_length <- nchar(my_name) 
print(name_length)
```

(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 
```{r}

```
(d) Define a function called `add_tree` that takes a single argument and returns a value 3 times larger than the input.
```{r}
add_tree
```
(e) Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.
```{r}
v1 <- 10:49
print(v1)
```
```{r}
length(v1)
```

(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.
```{r}
x_range <- seq(-5, 10, 0.5)
print(x_range)
```

